\chapter{General Guidlines}

\section{Title of the club}
Official name recommended as \textbf{ROBOCEK, ROBOTICS INTEREST GROUP,GOVERNMENT COLLEGE OF ENGINEERING KANNUR}


\section{Purpose}
The purpose of these bylaws is to ensure the successful implementation of themission and purpose of the ROBOCEK. These bylaws shall be established asthe official governing document for the ROBOCEK. However, in the event thatany policy in this document represents a conflict with a higher policy, such as thatof Government policy, college rules and regulations, the higher policy shall take
precedence over this document.


\section{Beliefs and Goals}
\subsection{Vision}
To devise a passionate community of strong responsible engineers technically skilled enough to figure out the need of the hour and act wisely to crack the challenges emphasizing the universal values.

\subsection{Mission}
Promote student learning in the fields of science, technology, engineering, mathematics, and marketing through hands-on team projects and collaboration with adult mentors and advisors who have experiences in their field of interest.
\par ROBOCEK may also participate in any other activities permissible to clubs and student organizations of GCE KANNUR.

\subsection{Values}
Strives to excel as a learning community by adapting, learning and relentlessly improving ourselves and the entire team by promoting initiatives devising healthy, ethical and social relations adhering to sustainable models of development.

\section{Time management}
For the proper working of the club without affecting much in their academicsections, class hours are exempted. Holidays and leisure time should be utilizedfor the work. In any special cases with the permission from an advisor with aconcerned letter can continue his work during class hours.

\section{Subgroups}
The officers and advisors shall establish various groups of students, known as“subgroups,” to complete various aspects of team projects. The elected officersare responsible for assigning or electing members to subgroups; a member mayparticipate in more than one subgroup at the discretion of the officers andadvisors. Each subgroup shall contain at least one student leader.The officersand advisor(s) have the power to form or disband additional subgroups oftemporary or permanent nature, provided that the above criteria are met in full.


\section{Meetings}

\subsection{Purpose}
ROBOCEK will, from time to time, hold both official and non-officialmeetings for the purposes of engaging in club activities and fulfilling itsmission.

\subsection{Official Meetings}
Official meetings are held in public locations or locations approved by theclub advisors. All official meetings must be supervised by at least one clubadvisor. Absence in official meetings is not encouraged and attendanceshall be recorded. The majority of work on team projects, as well all criticalclub functions (such as election, auditing reports), must be completedduring official meetings. The minutes of the meeting shall be recorded andproduced by the Secretary. The meeting shall be conducted at least onceevery month to detail upcoming plans.

\subsection{Non-Official Meetings}
Additional, non-official meetings may be held to complete work on teamprojects in smaller groups. It is the responsibility of the participants of the non-official meeting to provide a suitable location and ensure anappropriate level of supervision. 

\section{Elections}
A minimum of once each academic year, the ROBOCEK will hold elections todetermine officers for the upcoming academic year and vote on other importantclub matters. Officers elected will begin their terms at the point of election andhold them until the next election unless they resign or are dismissed. In any
special case the governing body can be extended with the permission of groupmembers and advisors.


\section{Conflict of Interest}
From time to time, situations may arise when an officer or advisor of the club mayhave an official, financial, personal, or otherwise conflicting interest with anofficial club matter of such nature that it may prevent acting rationally and impartially. In such a situation, they must find a solution in a decent mannerwhich would not affect the management of the group.

\section{Nondiscrimination Policy}
The officers, mentors, advisors, members, and affiliates of the ROBOCEK maynot discriminate on the basis of race, color, creed, disability, ethnicity, gender,
nationality, sexual orientation, or economic status. When possible, theROBOCEK should make arrangements to ensure that each student has an equalopportunity to gain a deeper understanding of the fields of science, technology,engineering, and mathematics.

\section{Dissolution}
Upon dissolution of ROBOCEK if and when the organization becomes defunct,any assets of the organization may be distributed for the educational purposes to
the GCE Kannur as determined by the officers and advisors. In this event, alltitles and memberships in the ROBOCEK shall be immediately considered void.

\section{Amendment}
These bylaws may be amended whenever required, ordered from the principalGCE KANNUR, requests from advisors ,2/3 of the active members proposedamendment is provided to the members at least one week in advance of themeeting where the vote is taken. Any member or advisor can propose such anamendment.
